### 2016-11-02 paper/evaluation.tex
minor change

\Jbc{Subject selection is currently OK but I will use another way (eg
Google BigQuery) to have access to more subjects.}We used the Github's
Search API~\cite{githubsearch} to fetch the top 1,000\footnote{The
    Search API imposes the limit of 1,000 results regardless of the
total number of matches from a search criteria.} Java projects with at
least 100 stars. The number of stars indicates the interest and
appreciation from the community to a given project.
\Comment{(https://help.github.com/articles/about-stars/)} Although our
criteria is subjective, it is an approximation to find relevant
projects to conduct our study. We detected the build manager system
based on the files located in the root directory from the project in
the following precedence: Maven (\emph{pom.xml)}, Gradle
(\emph{gradlew}), and Ant (\emph{build.xml}).\Jbc{Remember to update
the following values after updating the subject selection approach.}
From the 1,000 downloaded projects, we detected the build system of
801 subjects (composed by 216 Maven, 564 Gradle, and 21 Ant projects)
and considered \Fix{154} projects that we were able to compile.
\Fix{We noticed that we are unable to compile other subjects because of
unsolved dependencies, other build systems are commonly related to a
particular platform (\eg, Gradle implied Android), or the build
process is based on user-defined tasks (\eg, Ant).}

>>>>

\Jbc{Subject selection is currently OK but I will use another way (eg
Google BigQuery) to have access to more subjects.}We used the Github's
Search API~\cite{githubsearch} to fetch the top 1,000\footnote{The
    Search API imposes the limit of 1,000 results regardless of the
number of matches from a search criteria.} Java projects with at
least 100 stars. The number of stars indicates the interest and
appreciation from the community to a given project.
\Comment{(https://help.github.com/articles/about-stars/)} Although our
criteria is subjective, it is an approximation to find relevant
projects to conduct our study. We detected the build manager system
based on the files located in the root directory from the project in
the following precedence: Maven (\emph{pom.xml)}, Gradle
(\emph{gradlew}), and Ant (\emph{build.xml}).\Jbc{Remember to update
the following values after updating the subject selection approach.}
From the 1,000 downloaded projects, we detected the build system of
801 subjects (composed by 216 Maven, 564 Gradle, and 21 Ant projects)
and considered \Fix{154} projects that we were able to compile.
\Fix{We noticed that we are unable to compile other subjects because of
unsolved dependencies, other build systems are commonly related to a
particular platform (\eg, Gradle implied Android), or the build
process is based on user-defined tasks (\eg, Ant).}
